Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-05-07 awipev-CO2.Rmd
Still availability of data

### **Data availability**
TO DO: add here an horizontal bar plot showing the percent availability of the data

```{r data availability, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
# function to express the number of quality flag in pefrcent for each variable
qflag <- function(x) {
  summary(as.factor(x))*100/length(x)
}
selected_nydata_minute <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/nydata_minute.rds")) %>%
dplyr::select(ends_with("_qf"), -dt_qf) 
nam <- selected_nydata_minute %>% names()
selected_nydata_minute %>% map(~qflag(.x))

s1 <- summary(as.factor(selected_nydata_minute$pco2_corr_qf))*100/length(selected_nydata_minute$pco2_corr_qf)
s2 <- summary(as.factor(selected_nydata_minute$sal_fb_qf))*100/length(selected_nydata_minute$sal_fb_qf)
s3 <- summary(as.factor(selected_nydata_minute$sal_insitu_ctd_qf))*100/length(selected_nydata_minute$sal_insitu_ctd_qf)
s4 <- summary(as.factor(selected_nydata_minute$temp_dur_qf))*100/length(selected_nydata_minute$temp_dur_qf)
s5 <- summary(as.factor(selected_nydata_minute$temp_fb_qf))*100/length(selected_nydata_minute$temp_fb_qf)
s6 <- summary(as.factor(selected_nydata_minute$temp_insitu_11m_qf))*100/length(selected_nydata_minute$temp_insitu_11m_qf)
s7 <- summary(as.factor(selected_nydata_minute$phINT_qf))*100/length(selected_nydata_minute$phINT_qf)
s8 <- summary(as.factor(selected_nydata_minute$phEXT_qf))*100/length(selected_nydata_minute$phEXT_qf)
z <- t(bind_rows(s1,s2,s3,s4,s5,s6,s7,s8))
colname(z) <- nam

qflag <- function(x) {
  summary(as.factor(x))*100/length(x)
}
qflags <- tibble(pco2_corr = s1,
                 sal_fb = s2,
                 sal_insitu_ctd = s3,
                 temp_dur = s4,
                 temp_fb = s5,
                 temp_insitu_11m = s6,
                 phINT = s7,
                 phEXT = s8)

  summarise_all(percentcumsum)
  dplyr::mutate_all(funs("percent"= cumsum(.)/100))
p <-  ggplot(data = selected_nydata_minute) +
  geom_bar(aes(x = as.factor(pco2_corr_qf)))
p
# rm(selected_nydata_minute)
```

>>>>

### **Data availability**
The data at one minute frequency were tagged with the following quality flags

+ 1: good data
+ 3: failing the date and time test
+ 4: data not usable according to manufacturer
+ 7: failing the regional range test 
+ 12: failing the spike test (NAs from despike)
+ 13: failing the gradient test
+ 15: instrument not deployed or operated
+ 16: acid flush
+ 99: failing the final visual inspection

* Despike using oce::despike with n=2, k=5761

```{r data availability, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
# function to express the number of quality flag in pefrcent for each variable
# qflag <- function(x, ...) {
#   tmp <- summary(as.factor(x))*100/length(x)
#   return(tmp)
# }
d <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/all_nydata_minute.rds")) %>%
dplyr::select(datetime, c(pco2_corr_qf, sal_fb_qf, sal_insitu_ctd_qf, 
                          temp_fb_qf, temp_insitu_11m_qf, ph_dur_qf, phINT_qf))

s1 <- summary(as.factor(d$pco2_corr_qf))*100/length(d$pco2_corr_qf)
s2 <- summary(as.factor(d$sal_fb_qf))*100/length(d$sal_fb_qf)
s3 <- summary(as.factor(d$sal_insitu_ctd_qf))*100/length(d$sal_insitu_ctd_qf)
s4 <- summary(as.factor(d$temp_fb_qf))*100/length(d$temp_fb_qf)
s5 <- summary(as.factor(d$temp_insitu_11m_qf))*100/length(d$temp_insitu_11m_qf)
# durafet and seafet started later
x <- filter(d, datetime >= "2017-08-29 10:00:00")
#s6 <- summary(as.factor(x$temp_dur_qf))*100/length(x$temp_dur_qf)
s7 <- summary(as.factor(x$ph_dur_qf))*100/length(x$ph_dur_qf)
x <- filter(d, datetime >= "2017-08-24 19:00:00")
s8 <- summary(as.factor(x$phINT_qf))*100/length(x$phINT_qf)
z <- t(bind_rows(s1,s2,s3,s4,s5,s7,s8)) %>%
  as.data.frame() %>%
         rownames_to_column(var = "flag") %>% 
         as_tibble()
labels <- c("Good", "Not usable", "Outside regional range", "Outliers (despike)", 
            "Failed visual inspection", "No data")
#colnames(z) <- c("flag", colnames(d)[-1]) # remove first col name (datetime)
colnames(z) <- c("Flag", "pCO2", "Salinity FerryBox", "In situ salinity", 
                 "Temperature FerryBox", "In situ temperature", "Durafet pH", "seaFET pH")
zz <- pivot_longer(z, -Flag)
p <-  ggplot(data = zz, aes(x = name, y = value, fill = Flag)) +
  geom_bar(position = position_stack(reverse = TRUE), stat="identity", width = 0.3) +
  #scale_y_reverse() +
  #discrete_scale(labels = labels) + 
  coord_flip() +
  geom_text(aes(label=round(value, digits = 0)), position = position_stack(0.5), size = 3) +
  labs(x="", y="", title = "Distribution (%) of quality flags", color = "Quality flag") +
  theme_bw()
p
rm(d)
```
